\textbf{NBA Party}

### 2017-07-01 init_model.rnw
Incorporated (some of) Charlie V2 changes.

load(file = 'tmp_data/covers_lines.RData')
## load(file = 'tmp_data/nmusician_estabs.RData')
load(file = 'tmp_data/population_by_county_year.RData')
## load(file = 'tmp_data/nba_musicians.RData')
load(file = 'tmp_data/nba_studios.RData')

@@

## nba.lines[, list(date, team, opponent, location, 
##              line, score, outcome, nhours.lgame, 
##              travel.dist, avg.age, nmusicians)]

@@

HOURS <- 24
## nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team & weekdays(date) %in% c('Saturday', 'Sunday'), log(nmusicians+1), 0)]
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) &
                nhours.lgame <= HOURS &
                last.game.loc != team]
nba.lines[, party.placebo := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) &
                nhours.lgame > HOURS &
                last.game.loc != team]

@@

\section{Possible confounders}
What if we pick up effects of a busy play schedule?
Aside from accounting for how much rest time a team is allowed in between games,
and travel distance between games, we're also interested to get a measure of
fatigue incurred on the court.
We account for this by bringing in minutes data, and counting the number of 
times the players run back and forth on the court. This is crudely measured
by the number of changes in posession. We back out this quantity.

@@

## nba.lines[,.N/2,by=list(season)]
stargazer(m0, m1, covariate.labels = c('party discrete', 'party continuous', 'lag changes in posession', 'logged travel distance', 'east-west travel direction', 'number hours rest time', 'time of game during day', 'home team effect', 'logged travel distance * east-west', 'Constant'),
          dep.var.labels = 'Meet the Spread')

@@

stargazer(mp, covariate.labels = c('party placebo', 'lag changes in posession', 'logged travel distance', 'east-west travel direction', 'number hours rest time', 'time of game during day', 'home team effect', 'logged travel distance * east-west', 'Constant'),
          dep.var.labels = 'Meet the Spread')

@@

##################################################
### Why drinking estabs doesn't work.
##################################################
load(file = 'tmp_data/nba_drinking.RData')
drinking <- copy(dt)
setnames(drinking, 'variable', 'ndrinks')
rm(dt)

tmpm <- musicians[, list(log.nmusicians = mean(log(nmusicians+1)),
                         log.population = mean(log(population))), 
                  by = team][order(log.nmusicians)] %>% na.omit
tmpd <- drinking[, list(log.ndrinks = mean(log(ndrinks+1))), 
                  by = team][order(log.ndrinks)] %>% na.omit
tmp <- merge(tmpm, tmpd, by = 'team')
setorder(tmp, log.nmusicians)

@@

<<echo=-1>>=
load(file = 'tmp_data/covers_lines_mlb.RData')
mlb.lines <- lines
mlb.lines[, party := ifelse(team != location & weekend == 1, log(nmusicians), 0)]

@@

m3 <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + log(travel.dist+1) + weekend,
         data = mlb.lines, family = 'binomial')
summary(m3)

@@

## stargazer(m3, covariate.labels = c('Continuous measure of nightlife',
##                                    'Bookmaker\'s odds', 'Home-team effect',
##                                    'Number of rest days', 'Logged travel distance',
##                                    'Weekend', 'Constant'), 
##           dep.var.capation = 'Probability of Winning')

@@

##################################################
### Party by team location
##################################################
load(file = 'tmp_data/nmusician_estabs_mlb.RData')
tmp <- musicians[, list(party.continuous = mean(log(nmusicians+1))), 
                 by = team][order(party.continuous)][!is.na(party.continuous)]

>>>>

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/population_by_county_year.RData')
load(file = 'tmp_data/studios_and_artists_nba.RData')

@@

@@

HOURS <- 24
## nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team & weekdays(date) %in% c('Saturday', 'Sunday'), log(nmusicians+1), 0)]

### We create a discrete indicator for party based on LA or NY. As well as a placebo (longer rest)
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) &
                nhours.lgame <= HOURS &
                last.game.loc != team]
nba.lines[, party.placebo := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) &
                nhours.lgame > HOURS &
                last.game.loc != team]

### We then create a continuous measure of nightlife. We rescale to 0-1 so it's comparable.
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party := party / max(party, na.rm = T)]

@@

\section{Possible confounders}
What if we pick up effects of a busy play schedule?
Aside from accounting for how much rest time a team is allowed in between games,
and travel distance between games, we're also interested to get a measure of
fatigue incurred on the court.
We account for this by bringing in minutes data, and counting the number of 
times the players run back and forth on the court. This is crudely measured
by the number of changes in posession. We back out this quantity by looking
at the number of three pointers and field goals made, the number of missed shots,
as well as the number of turnovers and rebounds.

@@

## nba.lines[,.N/2,by=list(season)]
stargazer(m0, m1, covariate.labels = c('Party discrete', 'Party continuous', 
                                       'Lag changes in posession', 
                                       'Logged travel distance', 
                                       'East-west travel direction', 
                                       'Number hours rest time', 
                                       'Time of game during day', 
                                       'Home team effect', 
                                       'Logged travel distance * east-west', 
                                       'Constant'),
          dep.var.labels = 'Meet the Spread')

@@

stargazer(mp, covariate.labels = c('party placebo', 'lag changes in posession', 'logged travel distance', 'east-west travel direction', 'number hours rest time', 'time of game during day', 'home team effect', 'logged travel distance * east-west', 'Constant'),
          dep.var.labels = 'Meet the Spread (NBA)')

@@

##################################################
### Why drinking estabs doesn't work. (NBA)
##################################################
load(file = 'tmp_data/alcohol_and_drinking_nba.RData')
drinking <- copy(dt)
setnames(drinking, 'variable', 'ndrinks')
rm(dt)

tmpm <- nba.lines[, list(log.nmusicians = mean(log(nmusicians+1), na.rm = T),
                         log.population = mean(log(population),   na.rm = T)), 
                  by = team][order(log.nmusicians)] %>% na.omit
tmpd <- drinking[, list(log.ndrinks = mean(log(ndrinks+1))), 
                  by = team][order(log.ndrinks)] %>% na.omit
tmp <- merge(tmpm, tmpd, by = 'team')
setorder(tmp, log.nmusicians)

@@

<<echo=-1>>=
load(file = 'tmp_data/covers_lines_mlb.RData')
mlb.lines <- lines

@@

mlb.lines[, party := ifelse(team != location & weekend == 1, log(nmusicians), 0)]
mlb.lines[, party := party / max(party, na.rm = T)]

### See what happens if we don't interact with weekend, i.e. no weekend effect.
mlb.lines[, party.now := ifelse(team != location, log(nmusicians), 0)]
mlb.lines[, party.now := party.now / max(party.now, na.rm = T)]

m3 <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + log(travel.dist+1) + weekend,
         data = mlb.lines, family = 'binomial')
summary(m3)
m4 <- update(m3, . ~ party.now + . - party)

@@

stargazer(m3, m4, covariate.labels = c('Continuous measure of nightlife',
                                       'Nightlife (no weekend interaction)', 
                                       'Bookmaker\'s odds', 'Home-team effect',
                                       'Number of rest days', 'Logged travel distance',
                                       'Weekend', 'Constant'), 
          dep.var.labels = 'Probability of Winning')

stargazer(m4, covariate.labels = c('Party placebo',
                                   'Bookmaker\'s odds', 'Home-team effect',
                                   'Number of rest days', 'Logged travel distance',
                                   'Weekend', 'Constant'), 
          dep.var.labels = 'Probability of Winning (MLB)')

@@

##################################################
### Party by team location
##################################################
load(file = 'tmp_data/studios_and_artists_mlb.RData')
setnames(dt, 'variable', 'nmusicians')

tmp <- dt[, list(party.continuous = mean(log(nmusicians+1))),
          by = team][order(party.continuous)][!is.na(party.continuous)]
